---
title: 'Assignment V: GitHub and the ticketmaster.com API'
author: "Christopher Forschner"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up a new GitHub repository

(1) Register on github.com in case you have not done this already.
(2) Initialize a new public repository for this assignment on GitHub.
(3) For the following exercises of this assignment, follow the standard Git workflow (i.e., pull the latest
version of the project to your local computer, then stage, commit, and push all the modifications that you
make throughout the project). Every logical programming step should be well documented on GitHub
with a meaningful commit message, so that other people (e.g., your course instructor) can follow and
understand the development history. You can do this either using Shell commands or a Git GUI of your
choice.
(4) In the HTML file that you submit, include the hyperlink to the project repository (e.g., https://github.
com/yourUserName/yourProjectName)

```{r}
git_url <- 'https://github.com/chrisfor97/Assignment05cf'
```
## Getting to know the API
(5) Visit the documentation website for the API provided by ticketmaster.com (see here). Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at rate limits.
Features of the Ticketmaster Discovery API: 
* Searching events by keyword in a certain location (lat/long)
* Getting events for a particular artist OR venue in a specific country/city/zip code/DMA/etc
* Getting hi-res images for a particular event or artist.
* Search events of a certain genre in a particular location for a certain promoter
* rate limits: 5000 API calls per day and rate limitation of 5 requests per second
    + increasing rate limit is also possible but specific conditions need to be fullfilled. However, for this Assignment, this is not necessary


(6) Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment. Even though this API key is not secret per se (it is publicly visible on the
API Explorer website), please comply to the common secrecy practices discussed in the lecture and the
tutorial: Treat the API key as a secret token. Your API key should neither appear in the code that you
are submitting nor in your public GitHub repository.

```{r}
library(jsonlite)
library(httr)
library(tidyverse)
library(rlist)
```

```{r}
source('ticketmaster_api.R')
```

#Interacting with the API - the basics
(7) Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract the content from the response object and inspect the resulting list. Describe what you can see.
```{r}
tickets_de <- GET('https://app.ticketmaster.com/discovery/v2/venues', 
                  query=list("apikey"=ticketmaster_key,
                             "countryCode"="DE",
                             "locale"="*",
                             'size'=499)) %>% content

total_pages<-as.numeric(tickets_de$page$totalPages)
pagesize<-as.numeric(tickets_de$page$size)
elements<-as.numeric(tickets_de$page$totalElements)

```
```{r}
#define a function for requesting data
requester <-function(pages){
  #enforce a rate limit
  Sys.sleep(0.2)
  #call the api an get the respective page
  requ_page <- tickets_de <- GET('https://app.ticketmaster.com/discovery/v2/venues', 
                  query=list("apikey"=ticketmaster_key,
                             "countryCode"="DE",
                             "locale"="*",
                             'page'=pages,
                             'size'=499)) %>% content #increasing to 499 per page so every element can be caught
  #return the search items in a list
  requ_page <-requ_page$`_embedded`$venues
}

```


(8) Extract the name, the *city*, the *postalCode* and *address*, as well as the *url* and the *longitude* and *latitude* of the venues to a data frame. This data frame should have the following structure:
```{r}
tickets_de2 <-requester(0)
#exctract variable names 
empty_df_list <- list()
for (i in 1:20){
  empty_df_list[[i]]<-data.frame()
}
empty_df_list[[1]]<-map(tickets_de2[[1]],~.x)%>% data.frame()
for(i in 2:20){
  empty_df_list[[i]]<-map(tickets_de2[[i]],~.x)%>% data.frame()
}

empty_df<-list.stack(empty_df_list,fill=TRUE)
tickets_df1<-map(tickets_de2,~.x)
varnames=colnames(tickets_df1)


total_pages<-as.numeric(tickets_de$page$totalPages)
pagesize<-as.numeric(tickets_de$page$size)
```

```{r}
tickets_df1 <- map(tickets_de2, as.data.frame) %>%
  map(~ complete(tibble(.x),)) %>% #replaces missing columns with a NA
  bind_rows() %>% 
  select(c('name','name.1','line1','location.longitude','location.latitude','url','postalCode'))%>%
  rename(city = name.1,
         address = line1,
         latitude = location.latitude,
         longitude = location.longitude)
```


## Interacting with the API - advanced
(9) Have a closer look at the list element named page. Did your GET request from exercise (7) return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first
20 out of several thousands of venues. Check the API documentation under the section Venue Search.
How can you request the venues from the remaining results pages? Iterate over the results pages and
perform GET requests for all venues in Germany. After each iteration, extract the seven variables name,
city, postalCode, address, url, longitude, and latitude. Join the information in one large
data frame. Print the first 10 rows and the shape of the resulting data frame. The resulting data frame
should look something like this (note that the exact number of search results may have changed since
this document has been last modified):

```{r}
#get all pages for venues in Germany
venueslist_de<-map(0:total_pages,requester)

venueslist_de2<-venueslist_de[-which(sapply(venueslist_de, is.null))] #removing all list entries where list type is null
de_length<-as.numeric(length(venueslist_de2))
```
```{r}
empty_df_list <- list()




```

```{r}
length(venueslist_de) 
elementno <- c()
for (i in 1:length(venueslist_de2)){
  elementno[i]<-length(venueslist_de2[[i]])
}
sum(elementno)
```

```{r}
#get all pages for venues in Germany
venueslist_de<-map(0:total_pages,requester)

venueslist_de2<-venueslist_de[-which(sapply(venueslist_de, is.null))] #removing all list entries where list type is null
de_length<-as.numeric(length(venueslist_de2))
#dropped the 26th page, because it caused Problems I could not find a solution for
venueslist_de3<-venueslist_de2[-26]
for (i in 1:25){
  venues_df2<-map(venueslist_de3[[i]], as.data.frame) %>%
  map(~ complete(tibble(.x),)) %>% #replaces missing columns with a NA
  bind_rows()%>% 
  select(c('name','name.1','line1','location.longitude','location.latitude','url','postalCode'))%>%
  rename(city = name.1,
         address = line1,
         latitude = location.latitude,
         longitude = location.longitude)
  venues_df<-rbind(venues_df,venues_df2) 
}
venues_df<-venues_df%>% distinct()
head(venues_df)
  
  


```
# Visualizing the extracted data

(10) Below, you can find code that produces a map of Germany. Add points to the map indicating the
locations of the event venues across Germany.
```{r}
ggplot() +
borders("world", "Germany", colour = "black", fill = "grey90") +
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))
```




















